---
name: Han
surname: Zhang
position: "Postdoctoral Research Fellow"
address: "Department of Psychology, University of Michigan"
www: sites.lsa.umich.edu/hanzh
email: "hanzh@umich.edu"
#orcid: 0000-0001-6087-0428
researchgate: Han_Zhang175
github: HanZhang-psych
twitter: \_HanZhang_
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```

# Research Interests

Attention; distraction; mind-wandering; eye movements

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "Postdoctoral Research Fellow, Department of Psychology",
  "Advisor: Dr. John Jonides",
  "06/2020-present",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Doctor of Philosophy, Education and Psychology",
  "Dissertation: Mind-wandering: What Can We Learn from Eye Movements?",
  "09/2014-05/2020",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Master of Science, Psychology",
  NA,
  "09/2014-04/2018",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Bachelor of Science, Psychology",
  NA,
  "09/2010-07/2014",
  "Beijing Normal University",
  "Beijing, China",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Advisor
  )
```

# Awards and Grants

```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2020', 'Stanley E. and Ruth B. Dimond Best Dissertation Award', 'School of Education, University of Michigan', 'Dissertation: Mind-wandering: What Can We Learn from Eye Movements?', NA,
  '2020', '2020 ProQuest Distinguished Dissertation Awards (Nomination)','School of Education, University of Michigan', 'Dissertation: Mind-wandering: What Can We Learn from Eye Movements?',NA,
  '2019', "Rackham One-Term Dissertation Fellowship", "Rackham Graduate School, University of Michigan",NA,'$17417',
  '2019', "Rackham Graduate Student Research Grant", "Rackham Graduate School, University of Michigan",NA,'$3000',
  '2019, 2018, 2017', "Rackham Conference Travel Grant","Rackham Graduate School, University of Michigan",NA,'$1050',
  '2018', "Rackham Summer Training Award","Rackham Graduate School, University of Michigan",NA,'$3700',
  '2017, 2015', "Professor & Mrs. Cho-Yee To Travel Grant","School of Education, University of Michigan",NA, '$500',
  '2014', "China National Scholarship","Ministry of Education of the People's Republic of China",NA, '$1500',
  '2014, 2013', "The First Rank Academic Scholarship","Faculty of Psychology, Beijing Normal University",NA,'$300',
  '2013', "Beijing Student Research and Entrepreneurial Action Plan","Beijing Municipal Commission of Education",NA,'$1500',
  '2012', "Undergraduate Student Research Grant","Faculty of Psychology, Beijing Normal University",NA,'$280',
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Peer-reviewed Publications

```{r}
bibliography_entries("Published.bib")
```

# Book Chapters

```{r}
bibliography_entries("Book_chapters.bib")
```

# Work in Progress 

```{r}
bibliography_entries("In_progress.bib")
```

# Selected Presentations

```{r}
bibliography_entries("Presentations.bib")
```

# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '09/2017 - 12/2017',
  "EDUC 391: Educational Psychology and Human Development",
  "Course design; weekly lectures; grading assignments and exams; office hours"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```


## Graduate Student Instructor

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '01/2020 - 04/2020',
  "PSYCH 457 : Research in Educational and Cross-Cultural Settings",
  "Grading student essays and exams; office hours; supervising student research projects",
  '01/2019 - 04/2019',
  "PSYCH 457 : Research in Educational and Cross-Cultural Settings",
  "Grading student essays and exams; office hours; supervising student research projects",
  '01/2018 - 04/2018',
  "PSYCH 111: Introduction to Psychology",
  "Three review sessions per week; grading assignments and exams; office hours",
  '01/2017 - 04/2017',
  "PSYCH 457 : Research in Educational and Cross-Cultural Settings",
  "Grading student essays and exams; office hours; supervising student research projects",
  '09/2016 - 12/2016',
  "PSYCH 240: Intro to Cognitive Psychology",
  "Three review sessions per week; grading assignments and exams; office hours",
  '01/2016 - 04/2016',
  "PSYCH 457 : Research in Educational and Cross-Cultural Settings",
  "Grading student essays and exams; office hours; supervising student research projects"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

## Program Assistant

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '2015 - 2019',
  "Global Course Connection: Beijing Normal University",
  "Supervising joint research projects between US and Chinese students; organizing student activities"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

# Professional Service

## Ad Hoc Reviewer

* Memory & Cognition
* NeuroImage
* Visual Cognition
* Cognitive Science
* Scientific Studies of Reading
* Frontiers in Psychiatry
* Psychological Research

# References

```{r}
tribble(
  ~ Name,
  ~ Title,
  ~ Contact,
  'John Jonides, Ph.D.',
  "Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan; Senior Editor, Psychological Science",
  "jjonides@umich.edu; 734-764-0192",
  'Kevin F. Miller, Ph.D.',
  "Professor of Psychology and Education,  University of Michigan",
  "kevinmil@umich.edu; 734-615-1800",
  'Priti Shah, Ph.D.',
  "Professor of Cognition & Cognitive Neuroscience and Educational Psychology, University of Michigan",
  "priti@umich.edu; 734-615-3745",
  'Kai S. Cortina, Ph.D.',
  "Professor of Psychology, University of Michigan",
  "schnabel@umich.edu; 734-615-3809"
) %>%
  detailed_entries(where = Contact,
                   with = Name,
                   what = Title) 
```