---
name: Han
surname: Zhang
position: "Postdoctoral Research Fellow"
address: "Department of Psychology, University of Michigan"
www: sites.lsa.umich.edu/hanzh
email: "hanzh@umich.edu"
#orcid: 0000-0001-6087-0428
researchgate: Han_Zhang175
github: HanZhang-psych
twitter: \_HanZhang_
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple sections
csl: apa-cv.csl # change this if you want to use other citation styles
bibliography_published: "Published.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
bibliography_underreview: "Under review.bib"
bibliography_inprep: "In prep.bib"
bibliography_presentations: "Presentations.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```

# Research Interests

Attention; distraction; mind-wandering; eye movements

# Education

```{r}
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral Research Fellow, Department of Psychology","Advisor: Dr. John Jonides","05/2020-present","University of Michigan","Ann Arbor, MI, USA",
  "Doctor of Philosophy, Combined Program in Education and Psychology", "Dissertation: Mind-wandering: What Can We Learn from Eye Movements?","09/2018-05/2020", "University of Michigan", "Ann Arbor, MI, USA",
    "Doctor of Philosophy, Combined Program in Education and Psychology", "Advisors: Drs. Kevin Miller & Kai Cortina","09/2018-05/2020", "University of Michigan", "Ann Arbor, MI, USA",
  "Master of Science, Combined Program in Education and Psychology", NA, "09/2014-05/2018", "University of Michigan", "Ann Arbor, MI, USA",
  "Bachelor of Science, Psychology", NA, "09/2010-06/2014", "Beijing Normal University", "Beijing, China",
) %>% 
  detailed_entries(what=Degree, when=Year, with=Institution, where=Where, why=Advisor)
```

# Awards and Grants

```{r}
tribble(
  ~Year, ~Name, ~Institution,
  2019, "Rackham One-Term Dissertation Fellowship ($17417)", "University of Michigan",
  2019, "Rackham Graduate Student Research Grant ($3000)", "University of Michigan",
  2019, "Rackham Conference Travel Grant ($1050)","University of Michigan",
  2018, "Rackham Summer Training Award ($3700)","University of Michigan",
  2018, "Rackham Conference Travel Grant ($800)","University of Michigan",
  2017, "Rackham Conference Travel Grant ($800)","University of Michigan",
  2017, "Professor & Mrs. Cho-Yee To Travel Grant ($500)","University of Michigan",
  2015, "Professor & Mrs. Cho-Yee To Travel Grant ($500)","University of Michigan",
  2014, "China National Scholarship ($1500)","Ministry of Education of the People's Republic of China",
  2014, "The First Rank Academic Scholarship ($300)","Beijing Normal University",
  2013, "The First Rank Academic Scholarship ($300)","Beijing Normal University",
  2013, "Beijing Student Research and Entrepreneurial Action Plan ($1500)","Beijing Municipal Commission of Education",
  2012, "Undergraduate Student Research Grant ($280)","Beijing Normal University",
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution
  )
```

# Publications

<!-- Notes: copy and paste the following block for any other bibliography sections with the same bibliography key matched that you assigned in YAML  -->
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup
<!-- Bib-printing block ends here. -->



# Manuscripts Under Review 

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_underreview}
:::

\endgroup


# Manuscripts In Preparation

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_inprep}
:::

\endgroup



# Selected Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_presentations}
:::

\endgroup


# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '09/2017 - 12/2017', "EDUC 391: Educational Psychology and Human Development","Course design; weekly lectures; grading assignments and exams; office hours"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```


## Graduate Student Instructor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '01/2020 - 05/2020', "PSYCH 457 : Research in Educational and Cross-Cultural Settings", "Grading student essays; office hours; supervising student research projects",
  '01/2019 - 04/2019',"PSYCH 457 : Research in Educational and Cross-Cultural Settings","Grading student essays; office hours; supervising student research projects",
  '01/2018 - 04/2018', "PSYCH 111: Introduction to Psychology","Three review sessions per week; grading assignments and exams; office hours",
  '01/2017 - 04/2017', "PSYCH 457 : Research in Educational and Cross-Cultural Settings","Grading student essays; office hours; supervising student research projects",
  '09/2016 - 12/2016', "PSYCH 240: Intro to Cognitive Psychology","Three review sessions per week; grading assignments and exams; office hours",
  '01/2016 - 04/2016', "PSYCH 457 : Research in Educational and Cross-Cultural Settings","Grading student essays; office hours; supervising student research projects"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```

## Program Assistant

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '05/2019',  "Global Course Connection: Beijing Normal University", "Supervising joint research projects between US and Chinese students; organizing student activities",
  '05/2017', 'Global Course Connection: Beijing Normal University',  "Supervising joint research projects between US and Chinese students; organizing student activities",
  '05/2016', "Global Course Connection: Beijing Normal University", "Supervising joint research projects between US and Chinese students; organizing student activities",
  '05/2015', "Global Course Connections: Beijing Normal University", "Supervising joint research projects between US and Chinese students; organizing student activities"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```


# References

```{r}
tribble(
  ~Name, ~Title, ~Contact,
  'John Jonides, Ph.D.',  "Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan; Senior Editor, Psychological Science", "jjonides@umich.edu; 734-764-0192",
  'Kevin F. Miller, Ph.D.',  "Professor of Psychology and Education,  University of Michigan", "kevinmil@umich.edu; 734-615-1800",
  'Priti Shah, Ph.D.',  "Professor of Cognition & Cognitive Neuroscience and Educational Psychology, University of Michigan", "priti@umich.edu; 734-615-3745",
  'Kai S. Cortina, Ph.D.',  "Professor of Psychology, University of Michigan", "schnabel@umich.edu; 734-615-3809"
) %>% 
  detailed_entries(
    where = Contact,
    with = Name, 
    what = Title
  )
```