%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Han}{Zhang}

\position{Postdoctoral Research Fellow}
\address{Department of Psychology, University of Michigan}

\email{\href{mailto:hanzh@umich.edu}{\nolinkurl{hanzh@umich.edu}}}
\homepage{sites.lsa.umich.edu/hanzh}
\researchgate{Han\_Zhang175}
\github{HanZhang-psych}
\twitter{\_HanZhang\_}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January 2021}
    {Han Zhang~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

Attention; distraction; mind-wandering; eye movements

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Postdoctoral Research Fellow, Department of Psychology}{University of Michigan}{Ann Arbor, MI, USA}{05/2020-present}{\begin{cvitems}
\item Advisor: Dr. John Jonides
\end{cvitems}}
    \cventry{Doctor of Philosophy, Combined Program in Education and Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2018-05/2020}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\item Advisors: Drs. Kevin Miller \& Kai Cortina
\end{cvitems}}
    \cventry{Master of Science, Combined Program in Education and Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2014-05/2018}{\vspace{-4mm}}
    \cventry{Bachelor of Science, Psychology}{Beijing Normal University}{Beijing, China}{09/2010-06/2014}{\vspace{-4mm}}
\end{cventries}

\hypertarget{awards-and-grants}{%
\section{Awards and Grants}\label{awards-and-grants}}

\begin{cventries}
    \cventry{University of Michigan}{Rackham One-Term Dissertation Fellowship (\$17417)}{2019}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Rackham Graduate Student Research Grant (\$3000)}{2019}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Rackham Conference Travel Grant (\$1050)}{2019}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Rackham Summer Training Award (\$3700)}{2018}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Rackham Conference Travel Grant (\$800)}{2018}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Rackham Conference Travel Grant (\$800)}{2017}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Professor \& Mrs. Cho-Yee To Travel Grant (\$500)}{2017}{}{\vspace{-4mm}}
    \cventry{University of Michigan}{Professor \& Mrs. Cho-Yee To Travel Grant (\$500)}{2015}{}{\vspace{-4mm}}
    \cventry{Ministry of Education of the People's Republic of China}{China National Scholarship (\$1500)}{2014}{}{\vspace{-4mm}}
    \cventry{Beijing Normal University}{The First Rank Academic Scholarship (\$300)}{2014}{}{\vspace{-4mm}}
    \cventry{Beijing Normal University}{The First Rank Academic Scholarship (\$300)}{2013}{}{\vspace{-4mm}}
    \cventry{Beijing Municipal Commission of Education}{Beijing Student Research and Entrepreneurial Action Plan (\$1500)}{2013}{}{\vspace{-4mm}}
    \cventry{Beijing Normal University}{Undergraduate Student Research Grant (\$280)}{2012}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_published}{}
\leavevmode\hypertarget{ref-zhang_scan-paths_2020}{}%
\textbf{Zhang}, H., Anderson, N. C., \& Miller, K. F. (2020). Refixation
patterns of mind-wandering during real-world scene perception.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{47}(1), 36--52.
\url{https://doi.org/10.1037/xhp0000877}

\leavevmode\hypertarget{ref-zhang_wandering_2020}{}%
\textbf{Zhang}, H., Miller, K. F., Sun, X., \& Cortina, K. S. (2020).
Wandering eyes: Eye movements during mind wandering in video lectures.
\emph{Applied Cognitive Psychology}, \emph{34}(2), 449--464.
\url{https://doi.org/10.1002/acp.3632}

\leavevmode\hypertarget{ref-zhang_missing_2019}{}%
\textbf{Zhang}, H., Qu, C., Miller, K. F., \& Cortina, K. S. (2020).
Missing the joke: Reduced rereading of garden-path jokes during
mind-wandering. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{46}(4), 638--648.
\url{https://doi.org/10.1037/xlm0000745}

\leavevmode\hypertarget{ref-zhang_how_2018}{}%
\textbf{Zhang}, H., Miller, K. F., Cleveland, R., \& Cortina, K. S.
(2018). How listening to music affects reading: Evidence from eye
tracking. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{44}(11), 1778--1791.
\url{https://doi.org/10.1037/xlm0000544}

\endgroup

\hypertarget{manuscripts-under-review}{%
\section{Manuscripts Under Review}\label{manuscripts-under-review}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_underreview}{}
\leavevmode\hypertarget{ref-zhang_meaning_2020}{}%
\textbf{Zhang}, H., Anderson, N. C., \& Miller, K. F. (2020).
\emph{Mind-wandering during scene perception: On the role of meaning and
salience}. \url{https://doi.org/10.31234/osf.io/9fc2u}

\endgroup

\hypertarget{manuscripts-in-preparation}{%
\section{Manuscripts In Preparation}\label{manuscripts-in-preparation}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_inprep}{}
\leavevmode\hypertarget{ref-zhang_visual_2020}{}%
\textbf{Zhang}, H., Abagis, T., \& Jonides, J. (2020).
\emph{Mind-wandering during visual search}.

\leavevmode\hypertarget{ref-zhang_what_2020}{}%
\textbf{Zhang}, H., \& Shah, P. (2020). \emph{What can your iPhone tell
about your everyday cognitive functioning? An exploratory study using
screen time}.

\endgroup

\hypertarget{selected-presentations}{%
\section{Selected Presentations}\label{selected-presentations}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_presentations}{}
\leavevmode\hypertarget{ref-zhang_scan-paths_2020}{}%
\textbf{Zhang}, H., Anderson, N. C., \& Miller, K. F. (2020, April).
\emph{Scan-paths of mind-wandering during real-world scene perception}.
\textbf{Graduate student research award}. The 92nd annual meeting of the
midwestern psychological association (conference canceled due to
covid-19), Chicago, IL, USA.

\leavevmode\hypertarget{ref-zhang_reduced_2019}{}%
\textbf{Zhang}, H., Qu, C., Miller, K. F., \& Cortina, K. S. (2019,
November). \emph{Reduced re-reading of garden-path jokes during mindless
reading}. Poster presented at the 60th psychonomic society annual
meeting, Montreal, Canada.

\leavevmode\hypertarget{ref-sun_when_2019}{}%
Sun, X., Shah, P., \& \textbf{Zhang}, H. (2019, June). \emph{When do
students suffer from mind wandering? The role of individual difference
and learning context}. Poster presented at SARMAC XIII, Cape Cod, MA,
USA.

\leavevmode\hypertarget{ref-zhang_mind-wandering_2019}{}%
\textbf{Zhang}, H., Miller, K. F., Cortina, K. S., \& Jiang, T. (2019,
June). \emph{Mind-wandering in college classrooms: A mobile eye-tracking
study}. Poster presented at SARMAC XIII, Cape Cod, MA, USA.

\leavevmode\hypertarget{ref-fischer_examining_2019}{}%
Fischer, A., \& \textbf{Zhang}, H. (2019, May). \emph{Examining the
effect of word predictability during mindless reading}. Poster presented
at the association for psychological science annual meeting, Washington
DC, USA.

\leavevmode\hypertarget{ref-hwang_eye_2019}{}%
Hwang, Y.-G., \textbf{Zhang}, H., \& Miller, K. F. (2019, May).
\emph{Eye movements of mind-wandering during scene viewing: Insights
from scan-paths}. Poster presented at the association for psychological
science annual meeting, Washington DC, USA.

\leavevmode\hypertarget{ref-zhang_what_2019}{}%
\textbf{Zhang}, H., \& Shah, P. (2019, May). \emph{What can iPhone's
screen time tell about your cognitive functioning?} Poster presented at
the association for psychological science annual meeting, Washington DC,
USA.

\leavevmode\hypertarget{ref-zhang_mind-wandering_2019-1}{}%
\textbf{Zhang}, H. (2019, April). \emph{Mind-wandering: What can we
learn from eye-movements?} Talk presented at combined program in
education and psychology brownbag, University of Michigan.

\leavevmode\hypertarget{ref-zhang_scan-paths_2019}{}%
\textbf{Zhang}, H., Miller, K. F., \& Sun, X. (2019, March).
\emph{Scan-paths of mind-wandering during video lectures}. Poster
presented at the international convention of psychological science,
Paris, France.

\leavevmode\hypertarget{ref-zhang_how_2018}{}%
\textbf{Zhang}, H., \& Miller, K. F. (2018, November). \emph{How
irrelevant speech affects reading: The role of word predictability}.
Poster presented at the 59th psychonomic society annual meeting, New
Orleans, LA, USA.

\leavevmode\hypertarget{ref-qu_all_2018}{}%
Qu, C., \& \textbf{Zhang}, H. (2018, May). \emph{All joking aside:
Mind-wandering impairs processing of garden-path jokes}. Poster
presented at the association for psychological science annual meeting,
San Francisco, CA.

\leavevmode\hypertarget{ref-zhang_wandering_2018}{}%
\textbf{Zhang}, H., Miller, K. F., \& Sun, X. (2018, May). \emph{The
wandering eyes: Mind-wandering during video lectures is associated with
oculomotor behaviors}. Poster presented at the association for
psychological science annual meeting, San Francisco, CA.

\leavevmode\hypertarget{ref-zhang_how_2016}{}%
\textbf{Zhang}, H., Miller, K. F., Cleveland, R., \& Cortina, K. S.
(2016, May). \emph{How listening to music affects reading: Evidence from
eye tracking}. Poster presented at the association for psychological
science annual meeting, Chicago, IL, USA.

\leavevmode\hypertarget{ref-zhang_how_2016-1}{}%
\textbf{Zhang}, H., \& Cleveland, R. (2016, March). \emph{How does
listening to music affect reading? An eye tracking study}. Talk
presented at combined program in education and psychology brownbag,
University of Michigan.

\endgroup

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{primary-instructor}{%
\subsection{Primary Instructor}\label{primary-instructor}}

\begin{cventries}
    \cventry{Course design; weekly lectures; grading assignments and exams; office hours}{EDUC 391: Educational Psychology and Human Development}{09/2017 - 12/2017}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{graduate-student-instructor}{%
\subsection{Graduate Student
Instructor}\label{graduate-student-instructor}}

\begin{cventries}
    \cventry{Grading student essays; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2020 - 05/2020}{}{\vspace{-4mm}}
    \cventry{Grading student essays; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2019 - 04/2019}{}{\vspace{-4mm}}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 111: Introduction to Psychology}{01/2018 - 04/2018}{}{\vspace{-4mm}}
    \cventry{Grading student essays; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2017 - 04/2017}{}{\vspace{-4mm}}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 240: Intro to Cognitive Psychology}{09/2016 - 12/2016}{}{\vspace{-4mm}}
    \cventry{Grading student essays; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2016 - 04/2016}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{program-assistant}{%
\subsection{Program Assistant}\label{program-assistant}}

\begin{cventries}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connection: Beijing Normal University}{05/2019}{}{\vspace{-4mm}}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connection: Beijing Normal University}{05/2017}{}{\vspace{-4mm}}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connection: Beijing Normal University}{05/2016}{}{\vspace{-4mm}}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connections: Beijing Normal University}{05/2015}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\hypertarget{ad-hoc-reviewer}{%
\subsection{Ad Hoc Reviewer}\label{ad-hoc-reviewer}}

\begin{itemize}
\tightlist
\item
  Journal of Experimental Psychology: General
\item
  Memory \& Cognition
\item
  NeuroImage
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{cventries}
    \cventry{Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan; Senior Editor, Psychological Science}{John Jonides, Ph.D.}{jjonides@umich.edu; 734-764-0192}{}{\vspace{-4mm}}
    \cventry{Professor of Psychology and Education,  University of Michigan}{Kevin F. Miller, Ph.D.}{kevinmil@umich.edu; 734-615-1800}{}{\vspace{-4mm}}
    \cventry{Professor of Cognition \& Cognitive Neuroscience and Educational Psychology, University of Michigan}{Priti Shah, Ph.D.}{priti@umich.edu; 734-615-3745}{}{\vspace{-4mm}}
    \cventry{Professor of Psychology, University of Michigan}{Kai S. Cortina, Ph.D.}{schnabel@umich.edu; 734-615-3809}{}{\vspace{-4mm}}
\end{cventries}

\end{document}
