%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Han}{Zhang}

\position{Postdoctoral Research Fellow}
\address{Department of Psychology, University of Michigan}

\email{\href{mailto:hanzh@umich.edu}{\nolinkurl{hanzh@umich.edu}}}
\homepage{sites.lsa.umich.edu/hanzh}
\googlescholar{ujW-lXkAAAAJ}
\researchgate{Han\_Zhang175}
\github{HanZhang-psych}
\twitter{\_HanZhang\_}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {December 2023}
    {Han Zhang~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

Attention; distraction; mind-wandering; eye movements

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Postdoctoral Research Fellow, Department of Psychology}{University of Michigan}{Ann Arbor, MI, USA}{06/2020-present}{\begin{cvitems}
\item Advisor: Dr. John Jonides
\end{cvitems}}
    \cventry{Doctor of Philosophy, Education and Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2014-05/2020}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\end{cvitems}}
    \cventry{Master of Science, Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2014-04/2018}{}\vspace{-4.0mm}
    \cventry{Bachelor of Science, Psychology}{Beijing Normal University}{Beijing, China}{09/2010-07/2014}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{awards-and-grants}{%
\section{Awards and Grants}\label{awards-and-grants}}

\hypertarget{since-postdoc}{%
\subsection{Since Postdoc}\label{since-postdoc}}

\begin{cventries}
    \cventry{Standard Grant, National Science Foundation}{Probing attentional allocation with a novel forced-response method}{2023}{\$659,877}{\begin{cvitems}
\item Role: Key Personnel (Postdoc)
\end{cvitems}}
    \cventry{R21, National Institute of Mental Health}{Investigating interference-control in ADHD using a novel forced-response method}{2023}{\$429,000}{\begin{cvitems}
\item Role: Key Personnel (Postdoc)
\end{cvitems}}
\end{cventries}

\hypertarget{before-postdoc}{%
\subsection{Before Postdoc}\label{before-postdoc}}

\begin{cventries}
    \cventry{School of Education, University of Michigan}{Stanley E. and Ruth B. Dimond Best Dissertation Award}{2020}{\$500}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\end{cvitems}}
    \cventry{School of Education, University of Michigan}{2020 ProQuest Distinguished Dissertation Awards (Nomination)}{2020}{}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham One-Term Dissertation Fellowship}{2019}{\$17417}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Graduate Student Research Grant}{2019}{\$3000}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Conference Travel Grant}{2019, 2018, 2017}{\$1050}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Summer Training Award}{2018}{\$3700}{}\vspace{-4.0mm}
    \cventry{School of Education, University of Michigan}{Professor \& Mrs. Cho-Yee To Travel Grant}{2017, 2015}{\$500}{}\vspace{-4.0mm}
    \cventry{Ministry of Education of the People's Republic of China}{China National Scholarship}{2014}{\$1500}{}\vspace{-4.0mm}
    \cventry{Faculty of Psychology, Beijing Normal University}{The First Rank Academic Scholarship}{2014, 2013}{\$300}{}\vspace{-4.0mm}
    \cventry{Beijing Municipal Commission of Education}{Beijing Student Research and Entrepreneurial Action Plan}{2013}{\$1500}{}\vspace{-4.0mm}
    \cventry{Faculty of Psychology, Beijing Normal University}{Undergraduate Student Research Grant}{2012}{\$280}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{peer-reviewed-articles}{%
\section{Peer-reviewed Articles}\label{peer-reviewed-articles}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-zhang_d_2023}{}}%
\textbf{Zhang, H.}, Miyake, A., Osborne, J., Shah, P., \& Jonides, J.
(2023). A d factor? Understanding trait distractibility and its
relationships with ADHD symptomatology and hyperfocus. \emph{PLOS ONE},
\emph{18}(10), e0292215.
\url{https://doi.org/10.1371/journal.pone.0292215}

\leavevmode\vadjust pre{\hypertarget{ref-osborne_association_2023}{}}%
Osborne, J. B., \textbf{Zhang, H.}, Carlson, M., Shah, P., \& Jonides,
J. (2023). The association between different sources of distraction and
symptoms of attention deficit hyperactivity disorder. \emph{Frontiers in
Psychiatry}, \emph{14}. \url{https://doi.org/10.3389/fpsyt.2023.1173989}

\leavevmode\vadjust pre{\hypertarget{ref-fansher_icon_2022}{}}%
Fansher, M., Adkins, T. J., Lalwani, P., Boduroglu, A., Carlson, M.,
Quirk, M., Lewis, R. L., Shah, P., \textbf{Zhang, H.}, \& Jonides, J.
(2022). Icon arrays reduce concern over COVID-19 vaccine side effects: A
randomized control study. \emph{Cognitive Research: Principles and
Implications}, \emph{7}(1), 38.
\url{https://doi.org/10.1186/s41235-022-00387-5}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_malleability_2021}{}}%
\textbf{Zhang, H.}, Abagis, T. R., \& Jonides, J. (2021). The
malleability of attentional capture. \emph{Visual Cognition},
\emph{29}(9), 571--574.
\url{https://doi.org/10.1080/13506285.2021.1915903}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_scene_2021}{}}%
\textbf{Zhang, H.}, Anderson, N. C., \& Miller, K. F. (2021). Scene
meaningfulness guides eye movements even during mind-wandering.
\emph{Attention, Perception, \& Psychophysics}.
\url{https://doi.org/10.3758/s13414-021-02370-6}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_pre-trial_2021}{}}%
\textbf{Zhang, H.}, \& Jonides, J. (2021). Pre-trial Gaze Stability
Predicts Momentary Slips of Attention. \emph{EMICS '21}.
\url{https://psyarxiv.com/bv2uc/}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_refixation_2020}{}}%
\textbf{Zhang, H.}, Anderson, N. C., \& Miller, K. F. (2020). Refixation
Patterns of Mind-wandering during Real-world Scene Perception.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{47}(1), 36--52.
\url{https://doi.org/10.1037/xhp0000877}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_wandering_2020}{}}%
\textbf{Zhang, H.}, Miller, K. F., Sun, X., \& Cortina, K. S. (2020).
Wandering eyes: Eye movements during mind wandering in video lectures.
\emph{Applied Cognitive Psychology}, \emph{34}(2), 449--464.
\url{https://doi.org/10.1002/acp.3632}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_missing_2020}{}}%
\textbf{Zhang, H.}, Qu, C., Miller, K. F., \& Cortina, K. S. (2020).
Missing the joke: Reduced rereading of garden-path jokes during
mind-wandering. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{46}(4), 638--648.
\url{https://doi.org/10.1037/xlm0000745}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_how_2018}{}}%
\textbf{Zhang, H.}, Miller, K. F., Cleveland, R., \& Cortina, K. S.
(2018). How listening to music affects reading: Evidence from eye
tracking. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{44}(11), 1778--1791.
\url{https://doi.org/10.1037/xlm0000544}

\hypertarget{book-chapters}{%
\section{Book Chapters}\label{book-chapters}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-michal_cognitive_2021}{}}%
Michal, A., Fansher, M., Xin, S., \textbf{Zhang, H.}, \& Shah, P.
(2021). Cognitive development: Methods and illustrative examples. In
\emph{The oxford handbook of educational psychology}. Oxford University
Press.

\hypertarget{under-review}{%
\section{Under Review}\label{under-review}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-adkins_what_2023}{}}%
Adkins, T. J., \textbf{Zhang, H.}, Jonides, J., \& Lee, T. G. (2023).
\emph{What happens after an error?} BioArXiv.
\url{https://doi.org/10.1101/2022.03.17.484792}

\leavevmode\vadjust pre{\hypertarget{ref-fansher_flatten_2023}{}}%
Fansher, M., Lalwani, P., Adkins, T. J., \textbf{Zhang, H.}, Carlson,
M., Boduroglu, A., Lewis, R. L., Jonides, J., \& Shah, P. (2023).
\emph{Flatten what curve? Helping people make sense of pandemic
incidence when public health messaging fails}.
\url{https://doi.org/10.1186/s41235-022-00387-5}

\leavevmode\vadjust pre{\hypertarget{ref-lee_forced-response_2023}{}}%
Lee, T. G., Sellers, J., Jonides, J., \& \textbf{Zhang, H.} (2023).
\emph{The forced-response method: A new chronometric approach to measure
conflict processing}. PsyArXiv.
\url{https://doi.org/10.31234/osf.io/byzqf}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_lingering_2023}{}}%
\textbf{Zhang, H.}, Abagis, T. R., Steeby, C. J., \& Jonides, J. (2023).
\emph{Lingering on distraction: Examining distractor rejection in adults
with ADHD}. PsyArXiv. \url{https://doi.org/10.31234/osf.io/cqe34}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_does_2023}{}}%
\textbf{Zhang, H.}, Miller, K. F., \& Jonides, J. (2023). \emph{Does
mind-wandering affect distractor suppression?} PsyArXiv.
\url{https://doi.org/10.31234/osf.io/2h6kw}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_temporal_2023}{}}%
\textbf{Zhang, H.}, Sellers, J., Lee, T. G., \& Jonides, J. (2023).
\emph{The Temporal Dynamics of Visual Attention}. PsyArXiv.
\url{https://doi.org/10.31234/osf.io/e4ktq}

\leavevmode\vadjust pre{\hypertarget{ref-zhang_association_2023}{}}%
\textbf{Zhang, H.}, Xin, S., \& Miyake, A. (2023). \emph{On the
association between the self-control scale and social desirability
measures: A meta-analysis and systematic review}. PsyArXiv.
\url{https://doi.org/10.31234/osf.io/j4vy8}

\hypertarget{selected-presentations}{%
\section{Selected Presentations}\label{selected-presentations}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-zhang_modeling_2023}{}}%
\textbf{Zhang, H.}, Sellers, J., Lee, T., \& Jonides, J. (2023,
November). \emph{Modeling the temporal dynamics of visual attention}.
{[}Talk session{]}. The psychonomic society's 64nd annual meeting. San
francisco, CA, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_pretrial_2023}{}}%
\textbf{Zhang, H.}, \& Jonides, J. (2023, July). \emph{Pretrial
stability predicts momentary lapses of attention}. {[}Talk session{]}.
The current issues in mind-wandering research conference. Heidelberg,
germany.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_how_2022}{}}%
\textbf{Zhang, H.}, Adkins, T., Lee, T., \& Jonides, J. (2022,
November). \emph{How does the priority map change over time?} {[}Talk
session{]}. The psychonomic society's 63nd annual meeting. Boston, MA,
USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_uncovering_2021}{}}%
\textbf{Zhang, H.}, Miyake, A., Shah, P., \& Jonides, J. (2021,
November). \emph{Uncovering the structure of individual differences in
distractibility}. {[}Talk session{]}. The psychonomic society's 62nd
annual meeting. Virtual conference.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_mind-wandering_2020}{}}%
\textbf{Zhang, H.}, Anderson, N. C., \& Miller, K. F. (2020, November).
\emph{Mind-wandering during scene perception: On the role of meaning and
salience}. {[}Poster session{]}. The psychonomic society's 61st annual
meeting. Virtual conference.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_scan-paths_2020}{}}%
\textbf{Zhang, H.}, Anderson, N. C., \& Miller, K. F. (2020, April).
\emph{Scan-paths of mind-wandering during real-world scene perception}.
{[}Graduate student research award{]}. The 92nd annual meeting of the
midwestern psychological association (conference canceled due to
covid-19).

\leavevmode\vadjust pre{\hypertarget{ref-zhang_reduced_2019}{}}%
\textbf{Zhang, H.}, Qu, C., Miller, K. F., \& Cortina, K. S. (2019,
November). \emph{Reduced re-reading of garden-path jokes during mindless
reading}. {[}Poster session{]}. The psychonomic society's 60th annual
meeting. Montreal, québec, canada.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_mind-wandering_2019-1}{}}%
\textbf{Zhang, H.}, Miller, K. F., Cortina, K. S., \& Jiang, T. (2019,
June). \emph{Mind-wandering in college classrooms: A mobile eye-tracking
study}. {[}Poster session{]}. SARMAC XIII. Cape cod, MA, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_what_2019}{}}%
\textbf{Zhang, H.}, \& Shah, P. (2019, May). \emph{What can iPhone's
screen time tell about your cognitive functioning?} {[}Poster
session{]}. The association for psychological science annual meeting.
Washington, DC, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_mind-wandering_2019}{}}%
\textbf{Zhang, H.} (2019, April). \emph{Mind-wandering: What can we
learn from eye-movements?} {[}Talk session{]}. The combined program in
education and psychology brownbag. Ann arbor, MI, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_scan-paths_2019}{}}%
\textbf{Zhang, H.}, Miller, K. F., \& Sun, X. (2019, March).
\emph{Scan-paths of mind-wandering during video lectures}. {[}Poster
session{]}. The international convention of psychological science.
Paris, france.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_how_2018}{}}%
\textbf{Zhang, H.}, \& Miller, K. F. (2018, November). \emph{How
irrelevant speech affects reading: The role of word predictability}.
{[}Poster session{]}. The psychonomic society's 59th annual meeting. New
orleans, LA, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_wandering_2018}{}}%
\textbf{Zhang, H.}, Miller, K. F., \& Sun, X. (2018, May). \emph{The
wandering eyes: Mind-wandering during video lectures is associated with
oculomotor behaviors}. {[}Poster session{]}. The association for
psychological science annual meeting. San francisco, CA, USA.

\leavevmode\vadjust pre{\hypertarget{ref-zhang_how_2016}{}}%
\textbf{Zhang, H.}, Miller, K. F., Cleveland, R., \& Cortina, K. S.
(2016, May). \emph{How listening to music affects reading: Evidence from
eye tracking}. {[}Poster session{]}. The association for psychological
science annual meeting. Chicago, IL, USA.

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{primary-instructor}{%
\subsection{Primary Instructor}\label{primary-instructor}}

\begin{cventries}
    \cventry{Course design; weekly lectures; grading assignments and exams; office hours}{EDUC 391: Educational Psychology and Human Development}{09/2017 - 12/2017}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{graduate-student-instructor}{%
\subsection{Graduate Student
Instructor}\label{graduate-student-instructor}}

\begin{cventries}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2020 - 04/2020}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2019 - 04/2019}{}{}\vspace{-4.0mm}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 111: Introduction to Psychology}{01/2018 - 04/2018}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2017 - 04/2017}{}{}\vspace{-4.0mm}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 240: Intro to Cognitive Psychology}{09/2016 - 12/2016}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2016 - 04/2016}{}{}\vspace{-4.0mm}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connection: Beijing Normal University}{2015 - 2019}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{grant-writing-experience}{%
\section{Grant-writing Experience}\label{grant-writing-experience}}

\begin{cventries}
    \cventry{R21, National Institute of Mental Health}{Investigating interference-control in ADHD using a novel forced-response method}{2022}{Funded}{\begin{cvitems}
\item Role: Conceptualization; original draft preparation; formal analysis; reviewing \& editing
\end{cvitems}}
    \cventry{National Science Foundation}{Probing attentional allocation with a novel forced-response method}{2022}{Funded}{\begin{cvitems}
\item Role: Conceptualization; original draft preparation; formal analysis; reviewing \& editing
\end{cvitems}}
    \cventry{Merck Investigator Studies Program}{Testing the efficacy of interactive decision aids on vaccine attitudes and uptake using a Bayesian precision estimates}{2022}{Pending}{\begin{cvitems}
\item Role: reviewing \& editing
\end{cvitems}}
    \cventry{National Science Foundation}{Uncovering mechanisms of interference-resolution with a novel forced-response method}{2022}{Not Funded}{\begin{cvitems}
\item Role: Conceptualization; original draft preparation; formal analysis; reviewing \& editing
\end{cvitems}}
    \cventry{National Science Foundation}{Dissecting Distractibility by the Capture of Attention}{2021}{Not Funded}{\begin{cvitems}
\item Role: Original draft preparation; formal analysis; reviewing \& editing
\end{cvitems}}
    \cventry{National Science Foundation}{Mitigating distraction from external and internal sources}{2020}{Not Funded}{\begin{cvitems}
\item Role: Original draft preparation; formal analysis; reviewing \& editing
\end{cvitems}}
    \cventry{R01, National Institute of Mental Health}{Failure to resist external and internal distraction in ADHD}{2019}{Not Funded}{\begin{cvitems}
\item Role: Formal analysis; original draft preparation; reviewing \& editing
\end{cvitems}}
\end{cventries}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\hypertarget{opam-object-perception-attention-and-memory-workshop-organizer}{%
\subsection{OPAM (Object Perception, Attention, and Memory) Workshop
Organizer}\label{opam-object-perception-attention-and-memory-workshop-organizer}}

\begin{itemize}
\tightlist
\item
  OPAM 31, November 16th 2023, San Francisco, CA, US
\item
  OPAM 32, November 20th 2024, New York City, NY, YS
\item
  \url{http://www.opam.net/}
\end{itemize}

\hypertarget{star-scholarship-transferable-skills-academia-research-scholars-mentor}{%
\subsection{STAR (Scholarship, Transferable skills, Academia \&
Research) Scholars
Mentor}\label{star-scholarship-transferable-skills-academia-research-scholars-mentor}}

\begin{itemize}
\tightlist
\item
  2018-2020, mentored underrepresented students on academic research
  engagement and transferable skills.
\item
  \url{https://lsa.umich.edu/psych/undergraduates/star-scholars-program.html}
\end{itemize}

\hypertarget{ad-hoc-reviewer}{%
\subsection{Ad Hoc Reviewer}\label{ad-hoc-reviewer}}

\begin{itemize}
\tightlist
\item
  Memory \& Cognition
\item
  NeuroImage
\item
  Visual Cognition
\item
  Cognitive Science
\item
  Scientific Studies of Reading
\item
  Frontiers in Psychiatry
\item
  Psychological Research
\item
  Cognition
\item
  Scientific Reports
\item
  Journal of Experimental Psychology: Human Perception and Performance
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{cventries}
    \cventry{Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan}{John Jonides, Ph.D.}{jjonides@umich.edu}{}{}\vspace{-4.0mm}
    \cventry{Professor of Psychology and Education, University of Michigan}{Kevin F. Miller, Ph.D.}{kevinmil@umich.edu}{}{}\vspace{-4.0mm}
    \cventry{Assistant Professor of Psychology, University of Michigan}{Taraz G. Lee, Ph.D.}{tarazlee@umich.edu}{}{}\vspace{-4.0mm}
    \cventry{Professor of Psychology, University of Colorado Boulder}{Akira Miyake, Ph.D.}{akira.miyake@colorado.edu}{}{}\vspace{-4.0mm}
\end{cventries}



\end{document}
