---
name: Han
surname: Zhang
position: "Postdoctoral Research Fellow"
address: "Department of Psychology, University of Michigan"
www: sites.lsa.umich.edu/hanzh
email: "hanzh@umich.edu"
#to get the orcid: 0000-0001-6087-0428
googlescholar: ujW-lXkAAAAJ
osf: nrtbk # currently vitae doesn't support osf in the yaml header, need to add \osf{nrtbk} in the .tex file manulaly
github: HanZhang-psych
twitter: \_HanZhang_
#researchgate: Han_Zhang175
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    keep_tex: true
    pandoc_args: ["--lua-filter=lua/strong.lua"]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```

# Research Interests

Visual attention; cognitive control; mind-wandering; learning in educational contexts

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "Postdoctoral Research Fellow, Department of Psychology",
  "Advisor: Dr. John Jonides",
  "06/2020-present",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Doctor of Philosophy, Education and Psychology",
  "Dissertation: Mind-wandering: What Can We Learn from Eye Movements?",
  "09/2014-05/2020",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Master of Science, Psychology",
  NA,
  "09/2014-04/2018",
  "University of Michigan",
  "Ann Arbor, MI, USA",
  "Bachelor of Science, Psychology",
  NA,
  "09/2010-07/2014",
  "Beijing Normal University",
  "Beijing, China",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Advisor
  )
```

# Awards and Grants

## Since Postdoc

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2023',
  'Probing Attentional Allocation with a Novel Forced-Response Method',
  'Standard Grant, National Science Foundation',
  'Role: Key Personnel (Postdoc)',
  '$659,877',
  '2023',
  'Investigating Interference-Control in ADHD Using a Novel Forced-Response Method',
  'R21, National Institute of Mental Health',
  'Role: Key Personnel (Postdoc)',
  '$429,000',
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

## Before Postdoc

```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2020', 'Stanley E. and Ruth B. Dimond Best Dissertation Award', 'School of Education, University of Michigan', 'Dissertation: Mind-wandering: What Can We Learn from Eye Movements?', '$500',
  '2020', '2020 ProQuest Distinguished Dissertation Awards (Nomination)','School of Education, University of Michigan', NA ,NA,
  '2019', "Rackham One-Term Dissertation Fellowship", "Rackham Graduate School, University of Michigan",NA,'$17417',
  '2019', "Rackham Graduate Student Research Grant", "Rackham Graduate School, University of Michigan",NA,'$3000',
  '2019, 2018, 2017', "Rackham Conference Travel Grant","Rackham Graduate School, University of Michigan",NA,'$1050',
  '2018', "Rackham Summer Training Award","Rackham Graduate School, University of Michigan",NA,'$3700',
  '2017, 2015', "Professor & Mrs. Cho-Yee To Travel Grant","School of Education, University of Michigan",NA, '$500',
  '2014', "China National Scholarship","Ministry of Education of the People's Republic of China",NA, '$1500',
  '2014, 2013', "The First Rank Academic Scholarship","Faculty of Psychology, Beijing Normal University",NA,'$300',
  '2013', "Beijing Student Research and Entrepreneurial Action Plan","Beijing Municipal Commission of Education",NA,'$1500',
  '2012', "Undergraduate Student Research Grant","Faculty of Psychology, Beijing Normal University",NA,'$280',
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Journal Articles

```{r}
bibliography_entries("Published.bib")
```

# Book Chapters and Conference Proceedings

```{r}
bibliography_entries("Other.bib")
```

# Under Review

```{r}
bibliography_entries("Under_review.bib")
```

# Selected Presentations

```{r}
bibliography_entries("Presentations.bib")
```

# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '09/2017 - 12/2017',
  "EDUC 391: Educational Psychology and Human Development",
  "Participated in course design; taught weekly lectures; graded assignments and exams; held office hours"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

## Graduate Student Instructor

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '01/2019 - 04/2019',
  "PSYCH 111: Introduction to Psychology",
  "Taught three one-hour classes per week; graded student essays and exams; held office hours",
  '09/2016 - 12/2016',
  "PSYCH 240: Introduction to Cognitive Psychology",
  "Taught three one-hour classes per week; graded student essays and exams; held office hours",
  '2016 - 2020',
  "PSYCH 457: Research in Educational and Cross-Cultural Settings",
  "Graded student essays and exams; held office hours; supervised student research projects",
  '2015 - 2019',
  "Global Course Connection: Beijing Normal University",
  "Supervised joint research projects between US and Chinese students; organized cultural exchange activities"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```


# Grant-writing Experience

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Outcome,
  '2024',
  'Expanding the Impact of the Annual Object Perpcetion, Attention, and Memory (OPAM) Conference',
  'National Science Foundation',
  'Role: Conceptualization; original draft preparation; reviewing & editing',
  'In preparation for submission',
  
  '2024',
  'Toward a Psychological and Neural Model of Conflict Resolution',
  'National Science Foundation',
  'Role: Conceptualization; original draft preparation; formal analysis; reviewing & editing',
  'Funded',
  
  '2023',
  'Investigating Interference-Control in ADHD Using a Novel Forced-Response Method',
  'R21, National Institute of Mental Health',
  'Role: Conceptualization; original draft preparation; formal analysis; reviewing & editing',
  'Funded',
  
  '2023',
  'Probing Attentional Allocation with a Novel Forced-Response Method',
  'National Science Foundation',
  'Role: Conceptualization; original draft preparation; formal analysis; reviewing & editing',
  'Funded',

  '2022',
  'Uncovering Mechanisms of Interference-Resolution with a Novel Forced-Response Method',
  'National Science Foundation',
  'Role: Conceptualization; original draft preparation; formal analysis; reviewing & editing',
  'Not Funded',
  
  '2021',
  'Dissecting Distractibility by the Capture of Attention',
  'National Science Foundation',
  'Role: Original draft preparation; formal analysis; reviewing & editing',
  'Not Funded',
  
  '2020',
  'Mitigating Distraction from External and Internal Sources',
  'National Science Foundation',
  'Role: Original draft preparation; formal analysis; reviewing & editing',
  'Not Funded',
  
  '2019',
  'Failure to Resist External and Internal Distraction in ADHD',
  'R01, National Institute of Mental Health',
  'Role: Formal analysis; original draft preparation; reviewing & editing',
  'Not Funded'
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Outcome
  ) 
```


# Professional Service
## Object Perception, Attention, and Memory (OPAM) Conference Organizer
- OPAM 31, November 16th 2023, San Francisco, CA, US
- OPAM 32, November 21th 2024, New York City, NY, YS
- http://www.opam.net/

## Undergraduate Research Opportunity Program (UROP) Mentor
- 2018 - current, mentored undergraduate students conducting research projects.
- Mentored students: Madelyn Evans (2018), Nicole Fraija (2018), Yun Gi Hwang (2019), Alexander Fischer (2019), Esha Brar (2023)

## STAR (Scholarship, Transferable skills, Academia & Research) Scholars Mentor
- 2018-2020, mentored underrepresented students on academic research engagement and transferable skills.
- https://lsa.umich.edu/psych/undergraduates/star-scholars-program.html

## Ad Hoc Reviewer
-   Memory & Cognition
-   NeuroImage
-   Visual Cognition
-   Cognitive Science
-   Scientific Studies of Reading
-   Frontiers in Psychiatry
-   Psychological Research
-   Cognition
-   Scientific Reports
-   Journal of Experimental Psychology: Human Perception and Performance
-   PLOS One
-   Journal of Memory and Language
-   Neurobiology of Aging

# References

```{r}
tribble(
  ~ Name,
  ~ Title,
  ~ Contact,
  'John Jonides, Ph.D.',
  "Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan",
  "jjonides@umich.edu",
  'Priti Shah, Ph.D.',
  "Department Chair, Arthur Thurnau Professor of Psychology, Education, and Information, University of Michigan",
  "priti@umich.edu",
  'Kevin F. Miller, Ph.D.',
  "Professor of Psychology and Education, University of Michigan",
  "kevinmil@umich.edu",
  'Akira Miyake, Ph.D.',
  "Professor of Psychology, University of Colorado Boulder",
  "akira.miyake@colorado.edu"
) %>%
  detailed_entries(where = Contact,
                   with = Name,
                   what = Title) 
```
